GSE158422: DNA methylation in Lung squamous cell carcinoma - gene methylation enrichment analysis - sensitivity analysis

### 2023-10-09 figs/GSE158422_sensitivity.Rmd
sensitivity good

>>>>

Downsample

```{r,al_down1,fig.height=10}

#medf already exists

SAMPLESIZES=c(2,3,6,10,16,22,30)

ssres <- lapply(SAMPLESIZES,function(n) {
  SEEDS <- seq(100,5000,100)
  dsres <- mclapply(SEEDS, function(SEED) {
    set.seed(SEED)
    mysample <- sample(1:37,n,replace=FALSE)*2
    mysample <- c(mysample,(mysample-1))
    mysample <- mysample[order(mysample)]
    design2 <- design[mysample,]
    design2 <- design2[,colSums(design2)>0]
    medf2 <- medf[,mysample]
    dmagg2 <- agglimma(medf2,design2)
    m2 <- as.data.frame(dmagg2$t)
    rownames(m2) <- rownames(dmagg2)
    colnames(m2) <- "t"
    alres2 <- ttenrich(m=m2,genesets=gs_symbols,cores=CORES)
    head(alres2)
    alsig2 <- subset(alres2,fdr<0.05)
    TOT=nrow(alsig)
    TP=length(which(rownames(alsig2) %in% rownames(alsig)))
    FP=length(which(!rownames(alsig2) %in% rownames(alsig)))
    TPES=mean(abs(alsig[which(rownames(alsig) %in% rownames(alsig2)),"t_mean"]))
    RES=c("TOT"=TOT,"TP"=TP,"FP"=FP,"TPES"=TPES)
    RES
  },mc.cores=2)
  do.call(rbind,dsres)
})

par(mfrow=c(3,1))

dots <- lapply(ssres,function(x) { x[,"TP"] })
boxplot(dots,names=SAMPLESIZES,col="white",ylab="no. true positives",xlab="sample size",cex=0)
beeswarm(dots,add=TRUE,pch=1,cex=0.6)
abline(h= ssres[[1]][1,1])

dots <- lapply(ssres,function(x) { x[,"FP"] })
boxplot(dots,names=SAMPLESIZES,col="white",ylab="no. false positives",xlab="sample size",cex=0)
beeswarm(dots,add=TRUE,pch=1,cex=0.6)

dots <- lapply(ssres,function(x) { x[,"TP"] })
TPdots <- do.call(rbind,dots)
dots <- lapply(ssres,function(x) { x[,"FP"] })
FPdots <- do.call(rbind,dots)
ratio <- t(TPdots/FPdots)
ratio <- lapply(1:ncol(ratio),function(i) {ratio[,i]})

boxplot(ratio,names=SAMPLESIZES,col="white",ylab="TP per FP",xlab="sample size",cex=0)
beeswarm(ratio,add=TRUE,pch=1,cex=0.6)
